Mean and variance functions used to simulate Gaussian data

### 2019-11-12 analysis/gaussian_signals.Rmd
wflow_publish("gaussian_signals.Rmd")

```{r specify-n}
n = 1024
t = 1:n/n
```

Define the Spikes mean function.

```{r define-spikes}
mu.s = spike.f(t)
```

Define the Bumps variance function.

```{r define-bumps}
pos = c(0.1, 0.13, 0.15, 0.23, 0.25, 0.4, 0.44, 0.65, 0.76, 0.78, 0.81)
hgt = 2.97/5 * c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
wth = c(0.005, 0.005, 0.006, 0.01, 0.01, 0.03, 0.01, 0.01, 0.005, 0.008, 0.005)
mu.b = rep(0, n)
for (j in 1:length(pos))
  mu.b = mu.b + hgt[j]/((1 + (abs(t - pos[j])/wth[j]))^4)
```

Define the Doppler mean function.

```{r define-doppler}
mu.dop     = dop.f(t)
mu.dop     = 3/(max(mu.dop) - min(mu.dop)) * (mu.dop - min(mu.dop))
mu.dop.var = 10 * dop.f(t)
mu.dop.var = mu.dop.var - min(mu.dop.var)
```

@@

Define the "Blip" mean function.

```{r define-blip}
mu.blip = blip.fn(t,"mean")
```

Define the "Corner" mean function.

```{r define-corner}
mu.cor = cor.fn(t,"mean")
```

@@

```{r define-mean}
mu.sp   = (1 + mu.s)/5
mu.bump = (1 + mu.b)/5
mu.blk  = 0.2 + 0.6 * (mu.blk - min(mu.blk))/max(mu.blk - min(mu.blk))
mu.ang  = (1 + mu.ang)/5
mu.dop  = (1 + mu.dop)/5
```

@@

```{r define-variance}
var1 = rep(1, n)
var2 = (1e-02 + 4 * (exp(-550 * (t - 0.2)^2) +
                     exp(-200 * (t - 0.5)^2) +
                     exp(-950 * (t - 0.8)^2)))
var3 = (1e-02 + 2 * mu.dop.var)
var4 = 0.01 + mu.b
var5 = 0.01 + 1 * (mu.cblk - min(mu.cblk))/max(mu.cblk)
var1 = var1/2
var2 = var2/max(var2)
var3 = var3/max(var3)
var4 = var4/max(var4)
var5 = var5/max(var5)
```

@@

@@

```{r plot-mean-functions, fig.height=10, fig.width=6}
theme_set(theme_cowplot())
plot.signal <- function (t, y, label)
  quickplot(t,y,geom = "line",color = I("darkorange"),
            xlab = "",ylab = "",main = label)
plot_grid(plot.signal(t,mu.sp,"Spikes (sp)"),
          plot.signal(t,mu.bump,"Bumps (bump)"),
          plot.signal(t,mu.blk,"Blocks (blk)"),
          plot.signal(t,mu.ang,"Angles (ang)"),
          plot.signal(t,mu.dop,"Doppler (dop)"),
          plot.signal(t,mu.blip,"Blip (blip)"),
          plot.signal(t,mu.cor,"Corner (cor)"),
		  nrow = 4,ncol = 2)
```

>>>>

```{r specify-n}
n <- 1024
t <- 1:n/n
```

@@

Define the mean functions.

```{r define-mean}
mu.sp   <- spike.fn(t,"mean")
mu.bump <- bumps.fn(t,"mean")
mu.dop  <- doppler.fn(t,"mean")
mu.blip <- blip.fn(t,"mean")
mu.cor  <- cor.fn(t,"mean")
```

@@

```{r define-mean-2}
mu.blk  = 0.2 + 0.6 * (mu.blk - min(mu.blk))/max(mu.blk - min(mu.blk))
mu.ang  = (1 + mu.ang)/5
```

@@

```{r define-variance}
var1 = rep(1, n)
var2 = (0.01 + 4 * (exp(-550 * (t - 0.2)^2) +
                     exp(-200 * (t - 0.5)^2) +
                     exp(-950 * (t - 0.8)^2)))
var3 <- doppler.fn(t,"var")
var4 <- bumps.fn(t,"var")
var5 = 0.01 + 1 * (mu.cblk - min(mu.cblk))/max(mu.cblk)
var1 = var1/2
var2 = var2/max(var2)
var5 = var5/max(var5)
```

@@

This function will be used to draw the mean and variance functions.

```{r define-plot-signal}
plot.signal <- function (t, y, label)
  quickplot(t,y,geom = "line",color = I("darkorange"),
            xlab = "",ylab = "",main = label)
```

@@

```{r plot-mean-functions, fig.height=10, fig.width=6}
theme_set(theme_cowplot())
plot_grid(plot.signal(t,mu.sp,"Spikes (sp)"),
          plot.signal(t,mu.bump,"Bumps (bump)"),
          plot.signal(t,mu.blk,"Blocks (blk)"),
          plot.signal(t,mu.ang,"Angles (ang)"),
          plot.signal(t,mu.dop,"Doppler (dop)"),
          plot.signal(t,mu.blip,"Blip (blip)"),
          plot.signal(t,mu.cor,"Corner (cor)"),
		  nrow = 4,ncol = 2)
```
